Back to ``Normal'' for the Disintegrating Planet Candidate KIC 12557548 b

### 2018-06-01 ms.tex
added a plot with the time series.

In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} that shows amplitudes are anti-correlated with

>>>>

Figure \ref{fig:tserPC1} shows the time series of the first principal component, which tracks well with the dot product with the average light curve.

\begin{figure*}[!hbtp]
\begin{centering}
\includegraphics[width=0.99\textwidth]{images/kepler/pc1_tser_w_quiescent.pdf}
\caption{The first principal component's time series.}\label{fig:tserPC1}
\end{centering}
\end{figure*}

In Figure \ref{fig:ampPeriodogram} we show the periodogram of amplitudes that have peaks at 0.654, 22.9, 153 and 750 days.
The 22.9 day peak is consistent with the \citet{kawahara2013starspots} and \citet{croll2015starspots} that shows amplitudes are anti-correlated with stellar flux.
As suggested in \citet{kawahara2013starspots}, the anti-correlation points to a physical mechanism for the disintegration - such as magnetic activity or high energy flux associated with spots causing disintegration on the planet.
